---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("tidyverse")
library("GenomicRanges")
library("viridis")
library("data.table")
library("RColorBrewer")
library("gridExtra")


serv.dir <- "/home/jason/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "revamp/"

analysis.dir <- work.dir %&% "analysis_files/"
plot.dir <- work.dir %&% "plots/"

cred.df <- fread(work.dir %&% "genetic_credible_sets/gencred.txt")
cred.df$Locus.ID <- cred.df$CondID

df <- fread(analysis.dir%&%"classified-loci_weighted_with-shared.txt")

```


# some examples of signals with predominant tissue signatures 

```{r}

(dplyr::select(df,-contains("assigned_")) %>% arrange(.,desc(islet)) %>% filter(.,islet > 0.9))$symbol %>% unique(.)
(dplyr::select(df,-contains("assigned_")) %>% arrange(.,desc(liver)) %>% filter(.,liver > 0.9))$symbol %>% unique(.)
(dplyr::select(df,-contains("assigned_")) %>% arrange(.,desc(adipose)) %>% filter(.,adipose > 0.9))$symbol %>% unique(.)
(dplyr::select(df,-contains("assigned_")) %>% arrange(.,desc(muscle)) %>% filter(.,muscle > 0.87))$symbol %>% unique(.)

```



# Develop "sharing" score

```{r}

df$sep.score <- map(1:dim(df)[1],function(i){
  vec <- df[i,2:6] %>% sort(.,decreasing=TRUE) %>% as.numeric(.)
  vec[1] - vec[2]
}) %>% as.numeric(.)
df$share.score <- 1-df$sep.score

df$num.snps <- map(1:dim(df)[1],function(i){
  id <- df[i,]$Locus.ID
  dim(filter(cred.df,CondID==id))[1]
}) %>% as.integer(.)

df$max.ppa <- map(df$Locus.ID,function(id){
  filter(cred.df,CondID==id)$PPA %>% max(.)
}) %>% as.numeric(.)

sum(df$sep.score > median(df$sep.score))
summary(df$sep.score)

```


## EDA 

Number of SNPs 
```{r}

ggplotRegression <- function (fit) {

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red") +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}



plt1 <- ggplot(data=df,aes(x=sep.score)) + 
  geom_histogram(color="black",fill=viridis(100)[45]) + 
  xlab("Difference between two highest TOA scores") +
  ylab("Count") + 
  theme(panel.background = element_rect(fill="grey95") )
ggsave(plot=plt1,filename = plot.dir %&% "pleio_eda_1.png",width=5,height=4)
ggsave(plot=plt1,filename = plot.dir %&% "pleio_eda_1.pdf",width=5,height=4)

plt2 <- ggplot(data=df,aes(x=num.snps,y=sep.score)) + 
  geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Number of credible SNPs") +
  ylab("Difference between two highest TOA scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95") )

df$logsnps <- log(df$num.snps,base=10)
plt2 <- ggplotRegression(lm(sep.score~logsnps,data=df))
plt2 <- plt2 + geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Log10 of Number of 99% Credible SNPs") +
  ylab("Difference between two highest TOA scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))

ggsave(plot=plt2,filename = plot.dir %&% "pleio_eda_2.png",width=5,height=4)
ggsave(plot=plt2,filename = plot.dir %&% "pleio_eda_2.pdf",width=5,height=4)

plt2b <- ggplotRegression(lm(sep.score~num.snps,data=df))
plt2b <- plt2b + 
  geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Number of 99% credible SNPs") +
  ylab("Difference between two highest TOA scores") + 
  coord_cartesian(xlim=c(0,500))  + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt2b,filename = plot.dir %&% "pleio_eda_2b.png",width=5,height=4)
ggsave(plot=plt2b,filename = plot.dir %&% "pleio_eda_2b.pdf",width=5,height=4)

cor.test(df$num.snps,df$sep.score)
lm(df$sep.score~df$num.snps) %>% summary(.)


```


Maximum PPA 

```{r}

plt3 <- ggplotRegression(lm(sep.score~max.ppa,data=df))
plt3 <- plt3 + 
  geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Maximum PPA") +
  ylab("Difference between two highest TOA scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt3,filename = plot.dir %&% "pleio_eda_3.png",width=5,height=4)
ggsave(plot=plt3,filename = plot.dir %&% "pleio_eda_3.pdf",width=5,height=4)


cor.test(df$max.ppa,df$sep.score)
lm(df$sep.score~df$max.ppa) %>% summary(.)


```


## "Shared" loci at 10% difference threshold


```{r}

a <- filter(df,sep.score<=0.10)
b <- filter(df,sep.score>0.10)
t.test(a$max.ppa,b$max.ppa)

```


Alternative plot according to bins 


```{r}

num_to_thresh <- function(ppa.vec,thr){
  count <- 0
  runsum <- 0
  for (ppa in ppa.vec){
    if (runsum < thr){
      runsum <- runsum+ppa
      count <- count + 1 
    }
  }
  return(count)
}

df$num.snps10 <- map(df$Locus.ID,function(id){
    sub <- filter(cred.df,CondID==id)
    ppa.vec <- sub$PPA %>% sort(.,decreasing = T)
    count <- 0
    runsum <- 0
    for (ppa in ppa.vec){
      if (runsum < 0.1){
        runsum <- runsum+ppa
        count <- count + 1 
      }
    }
    count
}) %>% as.integer(.)
df$num.snps50 <- map(df$Locus.ID,function(id){
    sub <- filter(cred.df,CondID==id)
    ppa.vec <- sub$PPA %>% sort(.,decreasing = T)
    count <- 0
    runsum <- 0
    for (ppa in ppa.vec){
      if (runsum < 0.5){
        runsum <- runsum+ppa
        count <- count + 1 
      }
    }
    count
}) %>% as.integer(.)
df$num.snps80 <- map(df$Locus.ID,function(id){
    sub <- filter(cred.df,CondID==id)
    ppa.vec <- sub$PPA %>% sort(.,decreasing = T)
    count <- 0
    runsum <- 0
    for (ppa in ppa.vec){
      if (runsum < 0.8){
        runsum <- runsum+ppa
        count <- count + 1 
      }
    }
    count
}) %>% as.integer(.)

df$logsnps10 <- log(df$num.snps10,base=10)
df$logsnps50 <- log(df$num.snps50,base=10)
df$logsnps80 <- log(df$num.snps80,base=10)


```


Alternative scheme for measuring sharing (ssds)


```{r}

df$ssd <- map(1:dim(df)[1],function(i){
  vec <- df[i,] %>% dplyr::select(.,one_of("islet","muscle","adipose","liver")) %>% as.numeric(.) %>% 
    sort(.,decreasing = T)
  d1 <- vec[1]-vec[2]; d2 <- vec[2]-vec[3]; d3 <- vec[3]-vec[4]
  ssd <- (d1^2) + (d2^2) + (d3^2)
}) %>% as.numeric(.)

```



```{r}

plt4 <- ggplot(data=df,aes(x=ssd)) + 
  geom_histogram(color="black",fill=viridis(100)[55]) + 
  xlab("Sum of squared differences between scores") +
  ylab("Count") + 
  theme(panel.background = element_rect(fill="grey95") )
ggsave(plot=plt4,filename = plot.dir %&% "pleio_eda_4.png",width=5,height=4)
ggsave(plot=plt4,filename = plot.dir %&% "pleio_eda_4.pdf",width=5,height=4)

plt5 <- ggplotRegression(lm(ssd~logsnps,data=df))
plt5 <- plt5 + geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Log10 of Number of 99% Credible SNPs") +
  ylab("Sum of squared differences between scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt5,filename = plot.dir %&% "pleio_eda_5.png",width=5,height=4)
ggsave(plot=plt5,filename = plot.dir %&% "pleio_eda_5.pdf",width=5,height=4)

plt5b <- ggplotRegression(lm(ssd~logsnps10,data=df))
plt5b <- plt5b + geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Log10 of Number of 10% Credible SNPs ") +
  ylab("Sum of squared differences between scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt5b,filename = plot.dir %&% "pleio_eda_5b.png",width=5,height=4)
ggsave(plot=plt5b,filename = plot.dir %&% "pleio_eda_5b.pdf",width=5,height=4)

plt5c <- ggplotRegression(lm(ssd~logsnps50,data=df))
plt5c <- plt5c + geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Log10 of Number of 50% Credible SNPs ") +
  ylab("Sum of squared differences between scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt5c,filename = plot.dir %&% "pleio_eda_5c.png",width=5,height=4)
ggsave(plot=plt5c,filename = plot.dir %&% "pleio_eda_5c.pdf",width=5,height=4)

plt5d <- ggplotRegression(lm(ssd~logsnps80,data=df))
plt5d <- plt5d + geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Log10 of Number of 80% Credible SNPs ") +
  ylab("Sum of squared differences between scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt5d,filename = plot.dir %&% "pleio_eda_5d.png",width=5,height=4)
ggsave(plot=plt5d,filename = plot.dir %&% "pleio_eda_5d.pdf",width=5,height=4)


plt6 <- ggplotRegression(lm(ssd~max.ppa,data=df))
plt6 <- plt6 + 
  geom_point(color="black",shape=21,alpha=0.6,fill=viridis(10)[4]) + 
  xlab("Maximum PPA") +
  ylab("Sum of squared differences between scores") + 
  geom_smooth(method='lm',color=viridis(10)[2]) + 
  theme(panel.background = element_rect(fill="grey95"),
        plot.title = element_text(size=9))
ggsave(plot=plt6,filename = plot.dir %&% "pleio_eda_6.png",width=5,height=4)
ggsave(plot=plt6,filename = plot.dir %&% "pleio_eda_6.pdf",width=5,height=4)






```




# Profile "shared" signals by fine-mapping resolution 

Fine-mapped to a single SNP

```{r}

divvy.df <- fread(analysis.dir%&%"annotation-divvy-weighted-unscaled.txt")

s.df <- filter(df,sep.score<=0.10) # Note using difference between top two as measure for specificity, threshold used is 0.10, more directly interpretable than SSD 
s.df$lead.snp <- map(s.df$Locus.ID,function(id){
  filter(cred.df,CondID==id)$lead.rsid %>% unique(.)
}) %>% as.character(.)


s.df$coding.score <- map(s.df$Locus.ID,function(id){
  val <- filter(divvy.df,Locus.ID==id) %>% dplyr::select(.,contains("coding")) %>%
    as.numeric(.) %>% sum(.)
}) %>% as.numeric(.) 

write.table(x=s.df,file=analysis.dir%&%"shared-signals-120.txt",
            sep="\t",quote=F,row.names=F)

s1.df <- filter(s.df,num.snps==1)

View(s1.df)


tab1.df <- dplyr::select(s1.df,one_of("lead.snp","symbol","num.snps","max.ppa",
                                      "coding.score","sep.score","ssd",
                                      "islet","muscle","adipose","liver","unclassified")) %>% 
  arrange(.,desc(coding.score),desc(islet)) 

names(tab1.df) <- c("Signal (i.e. lead SNP rsid)","Gene Symbol", "Number of SNPs in 99% credible set",
                    "Maximum credible set PPA", "Coding Score",
                    "Dissimilarity (difference between top two TOA scores)",
                    "Sum of squared TOA score differences (SSD)",
                    "Islet TOA score","Muscle TOA score","Adipose TOA score","Liver TOA score",
                    "Unclassified TOA score")
write.table(x=tab1.df,file=analysis.dir%&%"SuppTable_shared_tier1.csv",quote=F,sep=",",row.names=F)

#names(tab1.df)[c(1,8)] <- c("signal.ID","dissimilarity")
#tab1.df$islet <- tab1.df$islet %>% prettyNum(.,digits=2)
#tab1.df$adipose <- tab1.df$adipose %>% prettyNum(.,digits=2)
#tab1.df$muscle <- tab1.df$muscle %>% prettyNum(.,digits=2)
#tab1.df$liver <- tab1.df$liver %>% prettyNum(.,digits=2)
#tab1.df$dissimilarity <- tab1.df$dissimilarity %>% prettyNum(.,digits=2)
#ggsave(grid.table(tab1.df),filename = plot.dir %&% "shared-single.png",
#       height=5,width=10)
#ggsave(grid.table(tab1.df),filename = plot.dir %&% "shared-single.pdf",
#       height=5,width=10)

```

Fine-mapped to more than one variant, but one variant accounts for >50% of PPA 

```{r}

s2.df <- filter(s.df,num.snps>1,max.ppa>0.5) # 23 signals, including lead signal at TCF7L2, and two signals at HNF4A

tab2.df <- dplyr::select(s2.df,one_of("lead.snp","symbol","num.snps","max.ppa",
                                      "coding.score","sep.score","ssd",
                                      "islet","muscle","adipose","liver","unclassified")) %>% 
  arrange(.,desc(coding.score),desc(islet)) 

names(tab2.df) <- c("Signal (i.e. lead SNP rsid)","Gene Symbol", "Number of SNPs in 99% credible set",
                    "Maximum credible set PPA", "Coding Score",
                    "Dissimilarity (difference between top two TOA scores)",
                    "Sum of squared TOA score differences (SSD)",
                    "Islet TOA score","Muscle TOA score","Adipose TOA score","Liver TOA score",
                    "Unclassified TOA score")
write.table(x=tab2.df,file=analysis.dir%&%"SuppTable_shared_tier2.csv",quote=F,sep=",",row.names=F)

#tab2.df <- dplyr::select(s2.df,one_of("Locus.ID","lead.snp","symbol","islet",
#                                   "muscle","adipose","liver","sep.score")) %>% 
#  arrange(.,desc(islet))
#names(tab2.df)[c(1,8)] <- c("signal.ID","dissimilarity")
#tab2.df$islet <- tab2.df$islet %>% prettyNum(.,digits=2)
#tab2.df$adipose <- tab2.df$adipose %>% prettyNum(.,digits=2)
#tab2.df$muscle <- tab2.df$muscle %>% prettyNum(.,digits=2)
#tab2.df$liver <- tab2.df$liver %>% prettyNum(.,digits=2)
#tab2.df$dissimilarity <- tab2.df$dissimilarity %>% prettyNum(.,digits=2)

#ggsave(grid.table(tab2.df),filename = plot.dir %&% "shared-mult-maxppa50.png",
#       height=10,width=10)
#ggsave(grid.table(tab2.df),filename = plot.dir %&% "shared-mult-maxppa50.pdf",
#       height=10,width=10)

```

Fine-mapped to more than one variant, but one variant accounts for >50% of PPA 

```{r}

s3.df <- filter(s.df,num.snps>1,max.ppa<=0.5) # 88 signals 

tab3.df <- dplyr::select(s3.df,one_of("lead.snp","symbol","num.snps","max.ppa",
                                      "coding.score","sep.score","ssd",
                                      "islet","muscle","adipose","liver","unclassified")) %>% 
  arrange(.,desc(coding.score),desc(islet)) 

names(tab3.df) <- c("Signal (i.e. lead SNP rsid)","Gene Symbol", "Number of SNPs in 99% credible set",
                    "Maximum credible set PPA", "Coding Score",
                    "Dissimilarity (difference between top two TOA scores)",
                    "Sum of squared TOA score differences (SSD)",
                    "Islet TOA score","Muscle TOA score","Adipose TOA score","Liver TOA score",
                    "Unclassified TOA score")
write.table(x=tab3.df,file=analysis.dir%&%"SuppTable_shared_tier3.csv",quote=F,sep=",",row.names=F)

#tab3.df <- dplyr::select(s3.df,one_of("Locus.ID","lead.snp","symbol","islet",
#                                   "muscle","adipose","liver","sep.score")) %>% 
#  arrange(.,desc(islet))
#names(tab3.df)[c(1,8)] <- c("signal.ID","dissimilarity")
#tab3.df$islet <- tab3.df$islet %>% prettyNum(.,digits=2)
#tab3.df$adipose <- tab3.df$adipose %>% prettyNum(.,digits=2)
#tab3.df$muscle <- tab3.df$muscle %>% prettyNum(.,digits=2)
#tab3.df$liver <- tab3.df$liver %>% prettyNum(.,digits=2)
#tab3.df$dissimilarity <- tab3.df$dissimilarity %>% prettyNum(.,digits=2)
#ggsave(grid.table(tab3.df),filename = plot.dir %&% "shared-mult-undermpp50.png",
#       height=40,width=10)
#ggsave(grid.table(tab3.df),filename = plot.dir %&% "shared-mult-undermpp50.pdf",
#       height=40,width=10)
```



## Deep dive into a given signal 


```{r}

an.df <- fread(analysis.dir%&%"annotation-divvy-weighted-unscaled.txt")
anall.df <- fread(analysis.dir%&%"annotation-divvy-weighted-unscaled_allSNPs.txt")


```


```{r}

get_sig_df <- function(sig){
  sub.df <- filter(anall.df,Locus.ID==sig)
  sub.df$ppa <- map(sub.df$SNPID,function(id,loc=sig){
    filter(cred.df,CondID==sig,SNPID==id)$PPA %>% max(.)
  }) %>% as.numeric(.)
  sub.df <- arrange(sub.df,desc(ppa))  
}

process_sig_snp <- function(sigsnp.df,ymax=1){
  snpid <- sigsnp.df$SNPID; ppa <- sigsnp.df$ppa
  test.df <- sigsnp.df[,3:(dim(sigsnp.df)[2]-1)]
  #test.df <- sub.df[1,3:(dim(sub.df)[2]-1)]
  annot <- test.df %>% names(.)
  val <- test.df %>% as.numeric(.)
  
  new.df <- data.frame(annot,val,stringsAsFactors = F)
  new.df$Annotation <- map(new.df$annot,function(a){
    strsplit(x=a,split="_")[[1]][1]
  }) %>% as.character(.)
  new.df$Tissue <- map(new.df$annot,function(a){
    strsplit(x=a,split="_")[[1]][2]
  }) %>% as.character(.)
  names(new.df) <- c("annot","score","Annotation","Tissue")
  new.df$Annotation <- factor(new.df$Annotation,
                              levels = c("coding","strongprom","weakprom",
                                         "flankprom","strongenh","weakenh",
                                         "genenh","stronggenetrans","weakgenetrans"))
  p <- ggplot(data=new.df,aes(x=Tissue,y=score)) + 
    geom_bar(aes(fill=Annotation),stat="identity",color="black") + 
    coord_cartesian(ylim=c(0,ymax)) + 
    scale_fill_manual(values=c("grey","firebrick1","firebrick3",
                               "firebrick4","gold1","gold3","yellowgreen",
                               "green1","green4")) + 
    theme_bw() + 
    ggtitle(snpid %&% "\nPPA="%&%round(ppa,3))
  return(list(p,new.df))
}


```


TCF7L2 lead signal 

```{r}

sig <- "130_1"

d <- get_sig_df(sig)
l1 <- process_sig_snp(d[1,],ymax=0.3)
l2 <- process_sig_snp(d[2,],ymax=0.3)
l3 <- process_sig_snp(d[3,],ymax=0.3)


p <- grid.arrange(l1[[1]],l2[[1]],l3[[1]],nrow=1)
write.table(x=d,file=analysis.dir%&%"signal_tcf7l2_130_1.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_tcf7l2_130_1.png",h=3.5,w=13)
ggsave(plot=p,filename = plot.dir %&% "signal_tcf7l2_130_1.pdf",h=3.5,w=12.5)


```

ANK1 Muscle signal 


```{r}

sig <- "106_3"
d <- get_sig_df(sig)

```




KCNJ11 lead signal 

```{r}

sig <- "135_1"

d <- get_sig_df(sig) # just doing the top 10 snps in credible set
l1 <- process_sig_snp(d[1,],ymax=0.3)
l2 <- process_sig_snp(d[2,],ymax=0.3)
l3 <- process_sig_snp(d[3,],ymax=0.3)
l4 <- process_sig_snp(d[4,],ymax=0.3)
l5 <- process_sig_snp(d[5,],ymax=0.3)
l6 <- process_sig_snp(d[6,],ymax=0.3)
l7 <- process_sig_snp(d[7,],ymax=0.3)
l8 <- process_sig_snp(d[8,],ymax=0.3)
l9 <- process_sig_snp(d[9,],ymax=0.3)
l10 <- process_sig_snp(d[10,],ymax=0.3)

p <- grid.arrange(l1[[1]],l2[[1]],l3[[1]],
                  l4[[1]],l5[[1]],l6[[1]],
                  l7[[1]],l8[[1]],l9[[1]],
                  l10[[1]],nrow=2,ncol=5)
write.table(x=d,file=analysis.dir%&%"signal_ank1_106_3.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_ank1_106_3.png",h=7,w=20)
ggsave(plot=p,filename = plot.dir %&% "signal_ank1_106_3.pdf",h=7,w=20)

sub <- dplyr::select(d[1:10,],one_of("SNPID","ppa"))
sub$chr <- map(sub$SNPID,function(s){
  strsplit(x=s,split=":")[[1]][1]
}) %>% as.character(.)
sub$pos0 <- map(sub$SNPID,function(s){
  as.integer(strsplit(x=s,split=":")[[1]][2]) - 1
}) %>% as.integer(.)
sub$pos <- map(sub$SNPID,function(s){
  as.integer(strsplit(x=s,split=":")[[1]][2]) - 1
}) %>% as.integer(.)
sub$ppa <- prettyNum(sub$ppa,digits=2)
sub$name <- "ANK1(PPA=" %&% sub$ppa %&% ")"
bed.df <- dplyr::select(sub,one_of("chr","pos0","pos","name"))

```

GCK lead signal 

```{r}

sig <- "95_1"

d <- get_sig_df(sig)
l1 <- process_sig_snp(d[1,],ymax=1)
l2 <- process_sig_snp(d[2,],ymax=1)


p <- grid.arrange(l1[[1]],l2[[1]],nrow=1)
write.table(x=d,file=analysis.dir%&%"signal_gck_95_1.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_gck_95_1.png",h=3.5,w=8)
ggsave(plot=p,filename = plot.dir %&% "signal_gck_95_1.pdf",h=3.5,w=8)


```


GCK secondary signal 

```{r}

sig <- "95_2"

d <- get_sig_df(sig)
l1 <- process_sig_snp(d[1,],ymax=0.3)
l2 <- process_sig_snp(d[2,],ymax=0.3)
l3 <- process_sig_snp(d[3,],ymax=0.3)
l4 <- process_sig_snp(d[4,],ymax=0.3)
l5 <- process_sig_snp(d[5,],ymax=0.3)

p <- grid.arrange(l1[[1]],l2[[1]],l3[[1]],l4[[1]],l5[[1]],nrow=1)
write.table(x=d,file=analysis.dir%&%"signal_gck_95_2.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_gck_95_2.png",h=3.5,w=20)
ggsave(plot=p,filename = plot.dir %&% "signal_gck_95_2.pdf",h=3.5,w=15)


```



CCND2 primary signal 

```{r}

sig <- "146_1"

d <- get_sig_df(sig)
l1 <- process_sig_snp(d[1,],ymax=0.6)

p <- grid.arrange(l1[[1]],nrow=1)
write.table(x=d,file=analysis.dir%&%"signal_ccnd1_146_1.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_ccnd1_146_1.png",h=3.5,w=5)
ggsave(plot=p,filename = plot.dir %&% "signal_ccnd1_146_1.pdf",h=3.5,w=5)


```


BCL2A primary signal 

```{r}

sig <- "210_1"

d <- get_sig_df(sig)
l1 <- process_sig_snp(d[1,],ymax=0.6)

p <- grid.arrange(l1[[1]],nrow=1)
write.table(x=d,file=analysis.dir%&%"signal_bcl2a_120_1.txt",sep="\t",quote=F,row.names=F)
ggsave(plot=p,filename = plot.dir %&% "signal_bcl2a_120_1.png",h=3.5,w=5)
ggsave(plot=p,filename = plot.dir %&% "signal_bcl2a_120_1.pdf",h=3.5,w=5)


```


