---
title: "01.1_tactical-toa-scores.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("tidyverse")
library("data.table")
#devtools::install_github("jmtorres138/TACTICAL")
library("TACTICAL")

serv.dir <- "/Users/jasont/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "tactical_analyses/rreb1/"
input.dir <- work.dir %&% "input_files/"
file.dir <- work.dir %&% "analysis_files/"

```




# TACTICAL Steps 1-4 


Annotate SNPs 

```{r}

snp.df <- annotate_snps(snp_file = input.dir%&%"credible-input.txt", 
                        tissue_path_file = input.dir%&%"tissue-file-paths.txt",
                        tissue_annotation_file = input.dir%&%"tissue-annotations.txt", 
                        genomic_path_file = input.dir%&%"genomic-file-paths.txt",
                        genomic_annotation_file = input.dir%&%"genomic-annotations.txt")
```


```{r}

#write.table(x=snp.df,file=file.dir%&%"annotated_snp-file.txt",quote=F,sep="\t",row.names=F)
write.table(x=snp.df,file=file.dir%&%"annotated_snp-file_osteo-dhs.txt",quote=F,sep="\t",row.names=F)

```


Calculate SNP scores 

```{r}
tvec.df <- calculate_tissue_vectors(snp.annotated.df = snp.df,
                                    tissue_annotation_file = input.dir%&%"tissue-annotations.txt", 
                                    genomic_annotation_file = input.dir%&%"genomic-annotations.txt")#,
                                    #ess.annot = "coding",
                                    #ess.file = input.dir%&%"gene-expression-specificity-scores.txt")
```

```{r}

#write.table(x=tvec.df,file=file.dir%&%"snp-score-file.txt",quote=F,sep="\t",row.names=F)
write.table(x=tvec.df,file=file.dir%&%"snp-score-file_osteo-dhs.txt",quote=F,sep="\t",row.names=F)

```

Calculate TOA scores 

```{r}

tscores.df <- calculate_toa_scores(snp.tissvec.df = tvec.df)

```


```{r}

#write.table(x=tscores.df,file=file.dir%&%"toa-scores.txt",quote=F,sep="\t",row.names=F)
write.table(x=tscores.df,file=file.dir%&%"toa-scores_osteo-dhs.txt",quote=F,sep="\t",row.names=F)

```



Tissue Classifier  

```{r}

class00.df <- tissue_classifier(toa.df=tscores.df, tissue_threshold = 0.0, shared_threshold = 0.1)
class20.df <- tissue_classifier(toa.df=tscores.df, tissue_threshold = 0.2, shared_threshold = 0.1)
class50.df <- tissue_classifier(toa.df=tscores.df, tissue_threshold = 0.5, shared_threshold = 0.1)
class80.df <- tissue_classifier(toa.df=tscores.df, tissue_threshold = 0.8, shared_threshold = 0.1)

```

  SIGNAL classification                               tissues
1   78_2     Osteoblast                            Osteoblast
2   78_3         Muscle                                Muscle
3   78_1         shared Adipose,Islet,Liver,Muscle,Osteoblast


-bash-4.2$ more toa-scores.txt 
SIGNAL	Adipose	Islet	Liver	Muscle	Osteoblast	unclassified
78_2	4e-04	0.0585	4e-04	0.0043	0.0849	0.8414
78_3	9e-04	9e-04	9e-04	0.2667	0.0018	0.722
78_1	0.1985	0.1985	0.1985	0.1985	0.1985	0
-bash-4.2$ more toa-scores_v1.txt 
SIGNAL	Adipose	Islet	Liver	Muscle	Osteoblast	unclassified
78_2	4e-04	0.0585	4e-04	0.0043	0.0849	0.8414
78_3	9e-04	9e-04	9e-04	0.2667	0.0018	0.722
78_1	0.1985	0.1985	0.1985	0.1985	0.1985	0
-bash-4.2$ more toa-scores_osteo-dhs.txt 
SIGNAL	Osteoblast	unclassified
78_2	0.0109	0.9791
78_3	0.0288	0.9646
78_1	0.9927	0


  Locus.ID     IndexSNP symbol        SNPID  CHR     POS     PPA coding CondID lead.rsid
1      121 chr6:7231843  RREB1 chr6:7231843 chr6 7231843 0.99266      1   78_1 rs9379084
NOTE: this maps coding but no "open chromatin" in ChIP-atlas 

INDEXSNP: rs112498319; note: 798 SNPs in credible set 
  Locus.ID     IndexSNP symbol        SNPID  CHR     POS      PPA coding CondID
1      119 chr6:7035734  RREB1 chr6:7035734 chr6 7035734 0.194430      0   78_2
2      119 chr6:7035734  RREB1 chr6:7109097 chr6 7109097 0.115610      0   78_2
3      119 chr6:7035734  RREB1 chr6:7033860 chr6 7033860 0.108780      0   78_2
4      119 chr6:7035734  RREB1 chr6:7037738 chr6 7037738 0.085869      0   78_2

INDEXSNP: rs9505097; note 22 SNPs in credible set 
  Locus.ID     IndexSNP symbol        SNPID  CHR     POS      PPA coding CondID
1      120 chr6:7255650  RREB1 chr6:7255650 chr6 7255650 0.184030      0   78_3
2      120 chr6:7255650  RREB1 chr6:7196323 chr6 7196323 0.143750      0   78_3
3      120 chr6:7255650  RREB1 chr6:7196324 chr6 7196324 0.135520      0   78_3
4      120 chr6:7255650  RREB1 chr6:7255610 chr6 7255610 0.067887      0   78_3



