---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("data.table"); library("tidyverse")
serv.dir <- "/Users/jasont/science/servers/FUSE5/"
work.dir0 <- serv.dir %&% "projects/t2d_classification/tactical_analyses/"
work.dir <- work.dir0 %&% "revisions/reviewer_1/"
input.dir <- work.dir0 %&% "input_files/"
analysis.dir <- work.dir %&% "analysis_files/"

```

```{r}

gtf.gr <- import(serv.dir %&% "datasets/gencode.v19.genes.v7.patched_contigs.gtf")
gtf.df <- as.data.table(gtf.gr,stringsAsFactors=FALSE)

```



```{r}

ess.df1 <- fread(input.dir %&% "expression_specificity_scores_v2.txt")
ess.df2 <- fread(analysis.dir %&% 
                   "expression_specificity_scores_v2-with-viscAdipose.txt")

```


```{r}

ess_process <- function(ess.df){
  out.df <- c()
  pb <- txtProgressBar(min=1,max=dim(ess.df)[1],style=3)
  for (i in 1:dim(ess.df)[1]){
    setTxtProgressBar(pb,i)
    row.df <- ess.df[i,]
    ensid <- row.df$GeneID
    sub.df <- gtf.df[gene_id==ensid & type=="gene" & gene_type=="protein_coding"]
    if (dim(sub.df)[1]>0){
      chrom <- "chr" %&% sub.df$seqnames
      start <- sub.df$start; end <- sub.df$end
      build.df <- data.frame("FEATURE_ID"=strsplit(ensid,split=".",fixed=TRUE)[[1]][1],
                             "FEATURE_NAME"=row.df$GeneName,"CHR"=chrom,"START"=start,"END"=end,
                             "Islet"=row.df$islet.score,
                             "Muscle"=row.df$muscle.score,
                             "Adipose"=row.df$adipose.score,
                             "Liver"=row.df$liver.score)
      out.df <- rbind(out.df,build.df)
    }    
  }
  return(na.omit(out.df))
}

```


```{r}

gess.df1 <- ess_process(ess.df1)
gess.df2 <- ess_process(ess.df2)

write.table(x=gess.df1,file = analysis.dir %&%
  "gene-expression-specificity-scores_v1.txt",sep="\t",quote=F,row.names=F)
write.table(x=gess.df2,file = analysis.dir %&% 
  "gene-expression-specificity-scores_v2.txt",sep="\t",quote=F,row.names=F)


```


```{r}
plot.df <- inner_join(gess.df1,gess.df2,by="FEATURE_ID")
plot(plot.df$Adipose.x,plot.df$Adipose.y)
```


```{r}

cor.test(plot.df$Adipose.x,plot.df$Adipose.y,method="pearson")

```


Pearson's product-moment correlation

data:  plot.df$Adipose.x and plot.df$Adipose.y
t = 294.43, df = 18128, p-value < 2.2e-16
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.9068735 0.9119094
sample estimates:
      cor 
0.9094248 


```{r}

cor.test(plot.df$Adipose.x,plot.df$Adipose.y,method="spearman")

```

Show in New WindowClear OutputExpand/Collapse Output
Cannot compute exact p-value with ties
	Spearman's rank correlation rho

data:  plot.df$Adipose.x and plot.df$Adipose.y
S = 9.0807e+10, p-value < 2.2e-16
alternative hypothesis: true rho is not equal to 0
sample estimates:
      rho 
0.9085729 

```{r}
cor.test(plot.df$Adipose.y,plot.df$Liver.x,method="spearman") # rho 0.001521062; p=0.8377
cor.test(plot.df$Adipose.y,plot.df$Islet.x,method="spearman") # rho -0.4255487 ; p-value < 2.2e-16
cor.test(plot.df$Adipose.y,plot.df$Muscle.x,method="spearman") # rho 0.02509856 ; 0.0007255

```

