---
title: "01.1_tactical-toa-scores.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("tidyverse")
library("data.table")
#devtools::install_github("jmtorres138/TACTICAL")
library("TACTICAL")

serv.dir <- "/Users/jasont/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "tactical_analyses/revisions/reviewer_1/"
input.dir <- work.dir %&% "input_files/"
file.dir <- work.dir %&% "analysis_files/"

toa.df1 <- fread(proj.dir %&% "tactical_analyses/analysis_files/" %&% 
                   "classified-loci_weighted_with-shared.txt")
toa.df2 <- fread(file.dir%&%"classified-loci_weighted_with-shared-adiVisc.txt")

```


```{r}

cor.test(toa.df1$adipose,toa.df2$adipose,method="pearson")

```

Show in New WindowClear OutputExpand/Collapse Output

	Pearson's product-moment correlation

data:  toa.df1$adipose and toa.df2$adipose
t = 221.32, df = 378, p-value < 2.2e-16
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.9953075 0.9968639
sample estimates:
      cor 
0.9961637 

```{r}

cor.test(toa.df1$adipose,toa.df2$adipose,method="spearman")

```

	Spearman's rank correlation rho

data:  toa.df1$adipose and toa.df2$adipose
S = 6381.4, p-value < 2.2e-16
alternative hypothesis: true rho is not equal to 0
sample estimates:
      rho 
0.9993022 


```{r}

table(toa.df1$assigned_20)
table(toa.df2$assigned_20)

toa.df1[!(toa.df1$assigned_20 == toa.df2$assigned_20)]

toa.df2[!(toa.df2$assigned_20 == toa.df1$assigned_20)]



```


