---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r}

"%&%" <- function(a,b) paste0(a,b)

library("tidyverse")
library("data.table")

serv.dir <- "/home/jason/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "method_C/"
file.dir <- proj.dir %&% "method_C/analysis_files/"
input.dir <- proj.dir %&% "analysis_files/"

full.df <- fread(file.dir %&% "islet-profile-all.txt")
isl.df <- fread(file.dir %&%  "islet-profile-IsletMaxPPA50.txt")

```


```{r}

(isl.df$coding > 0.1) %>% sum(.)
filter(isl.df,coding>=0.10) %>% arrange(.,desc(coding)) 

```

Of the 51 islet classified, 8 have signficant coding scores (>10%) and include PAM (2), PATJ (1), RREB1 (1), NEUROG3 (4), FAM57B (2), POC5 (1), SLC30A8 (1), QSER (1) 


```{r}
library("viridis")
vircols <- viridis(100)


plt.df1 <- filter(isl.df,islet>0.1,coding < 0.10) # 16
sum(plt.df1$islet>.50) # 15 
# filter(plt.df1,islet>0.5)

plt.df1$Signal <- plt.df1$symbol %&% " (" %&% plt.df1$Locus.ID %&% ")" %>%
  as.factor(.)
plt.df1$Signal <- factor(plt.df1$Signal,levels=arrange(plt.df1,desc(islet))$Signal)

plt1 <- ggplot(data = plt.df1, aes(x=Signal,y=islet)) + 
  geom_bar(stat="identity",size=1.2,color="black",fill=vircols[40]) + 
  ylab("Islet Open Chromatin Score") + 
  theme(axis.text.x=element_text(angle=90,vjust = .5)) + 
  scale_y_continuous(breaks=seq(0,1,0.1))

ggsave(plot=plt1,filename = work.dir %&% "plots/islet-atac-scores.png",
       height = 4,width=10)
ggsave(plot=plt1,filename = work.dir %&% "plots/islet-atac-scores.pdf",
       height = 4,width=10)

  
```

There are 16 (of the 51 islet clasified loci) credible sets that overlap islet open chromatin ATAC and account for more than 10% of cumulative PPA and have coding < 10%; 15 of which have majority of PPA mapping to open islet chromatin  



```{r}

build_pltdf2 <- function(plt.df1){
  out.df <- c()
  for (i in 1:dim(plt.df1)[1]){
    row.df <- plt.df1[i,]
    Type <- c("endocrine","exocrine")
    Score <- dplyr::select(row.df,one_of(Type)) %>% as.numeric(.)
    build.df <- data.frame(Signal=row.df$Signal,Type,Score)
    out.df <- rbind(out.df,build.df)
  }
  return(out.df)
}

```

```{r}
plt.df2 <- build_pltdf2(plt.df1) #%>% filter(.,Score>0.0001)
plt2 <- ggplot(data = plt.df2, aes(x=Signal,y=Score,fill=Type)) + 
  geom_bar(stat="identity",color="black") + 
  ylab("Differentially Open Chromatin Score") + 
  theme(axis.text.x=element_text(angle=90,vjust = .5)) + 
  scale_y_continuous(breaks=seq(0,1,0.1)) + 
  scale_fill_manual(values=c(vircols[40],vircols[90]))

ggsave(plot=plt2,filename = work.dir %&% "plots/islet-diff-atac-scores.png",
       height = 5,width=10)
ggsave(plot=plt2,filename = work.dir %&% "plots/islet-diff-atac-scores.pdf",
       height = 5,width=10)
```


Of the 36, 2 signals overlap regions that have differentially open chromatin in endocrine islet tissue, both at ANKH (4 and 5 signals) 


```{r}

build_pltdf3 <- function(plt.df1){
  out.df <- c()
  for (i in 1:dim(plt.df1)[1]){
    row.df <- plt.df1[i,]
    Type <- c("alpha","beta","duct")
    Score <- dplyr::select(row.df,one_of(Type)) %>% as.numeric(.)
    build.df <- data.frame(Signal=row.df$Signal,Type,Score)
    out.df <- rbind(out.df,build.df)
  }
  return(out.df)
}

```


```{r}

plt.df3 <- build_pltdf3(plt.df1) #%>% filter(.,Score>0)
plt3 <- ggplot(data = plt.df3, aes(x=Signal,y=Score,fill=Type)) + 
  geom_bar(stat="identity",color="black") + 
  ylab("Differentially Open Chromatin Score") + 
  theme(axis.text.x=element_text(angle=90,vjust = .5)) + 
  scale_y_continuous(breaks=seq(0,1,0.1)) + 
  scale_fill_manual(values=c(vircols[60],vircols[40],vircols[90]))

ggsave(plot=plt3,filename = work.dir %&% "plots/islet-diff-atacCELLS-scores.png",
       height = 5,width=10)
ggsave(plot=plt3,filename = work.dir %&% "plots/islet-diff-atacCELLS-scores.pdf",
       height = 5,width=10)
```


The primary signal at FAM49A is differentially open in beta cells, whereas the ninth signal at KCNQ1 is differentially open in alpha cells 

