---
title: "Divvy coding PPA"
author: "Jason Torres"
date: "January 8, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup 

```{r}

"%&%" <- function(a,b) paste0(a,b)

library("tidyverse")
library("data.table")
library("Homo.sapiens")

serv.dir <- "/Users/jtorres/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "method_A/"
out.dir <- work.dir %&% "analysis_files/"
ess.dir <- proj.dir %&% "analysis_files/"

ess.df <- fread(ess.dir %&% "expression_specificity_scores.txt")
blk.df <- fread(work.dir %&% "multi_results/results_blocks.txt")
ppa.df <- fread(out.dir %&%"full_best-joint_ppa-prop.txt")


sym.ids <- unique(keys(Homo.sapiens, keytype = "SYMBOL"))
sym.df <- select(Homo.sapiens,key=sym.ids,keytype="SYMBOL",
                 columns=c("ENSEMBL")) 

```


# Determine number of loci will not be able to be directly evaluated (will uniformly divvy ppa for these loci)

```{r}

locid_to_symbol <- function(locid){
  return(filter(blk.df,Locus.ID==locid)$refseq %>% as.character(.))
}


check <- map(ppa.df$Locus.ID,function(locid){
  sym <- locid_to_symbol(locid)
  sub <- filter(ess.df,GeneName==sym)
  if (dim(sub)[1] == 0){
    ensid <- filter(sym.df,SYMBOL==sym)$ENSEMBL %&% "." 
    if (length(ensid) > 1){
      sub1 <- filter(ess.df,grepl(pattern=ensid[1],GeneID,fixed=TRUE))
      sub2 <- filter(ess.df,grepl(pattern=ensid[2],GeneID,fixed=TRUE))
      sub <- rbind(sub1,sub2)
    } else{
      sub <- filter(ess.df,grepl(pattern=ensid,GeneID,fixed=TRUE))
    }
  }
  if (dim(sub)[1] == 1){
    return(NA)
  } else{
    print(c(locid,sym))
    return(filter(ppa.df,Locus.ID==locid)$coding)
  }}) %>% as.numeric(.) %>% na.omit(.)


```


There are 23 loci that can't be linked to an ensid with ESS information, however, the max PPA is only 0.10 and the median and mean are 0 and 0.12, respectively. Therefore, don't expect this will have a meaningful effect on the results (especially since PPA will be divvied uniformly)

# Divvy coding PPA 


```{r}

divvy_coding_ppa <- function(locid){
  sym <- locid_to_symbol(locid)
  sub <- filter(ess.df,GeneName==sym)
  if (dim(sub)[1] == 0){
    ensid <- filter(sym.df,SYMBOL==sym)$ENSEMBL %&% "." 
    if (length(ensid) > 1){
      sub1 <- filter(ess.df,grepl(pattern=ensid[1],GeneID,fixed=TRUE))
      sub2 <- filter(ess.df,grepl(pattern=ensid[2],GeneID,fixed=TRUE))
      sub <- rbind(sub1,sub2)
    } else{
      sub <- filter(ess.df,grepl(pattern=ensid,GeneID,fixed=TRUE))
    }
  }
  codeval <- filter(ppa.df,Locus.ID==locid)$coding
  if (dim(sub)[1] == 1){
    score.vec <- c(sub$islet.score,sub$muscle.score,sub$adipose.score,sub$liver.score)
  } else{
    score.vec <- c(0.25,0.25,0.25,0.25)
  }
  divvy.vec <- codeval * score.vec
  out.df <- data.frame(Locus.ID=locid,islet.coding=divvy.vec[1],muscle.coding=divvy.vec[2],
                       adipose.coding=divvy.vec[3],liver.coding=divvy.vec[4],stringsAsFactors = FALSE)  
}


build_coding_divvy_df <- function(){
  locids <- ppa.df$Locus.ID
  out.df <- c()
  pb <- txtProgressBar(min=0,max=length(locids),style=3)
  for (i in 1:length(locids)){
    setTxtProgressBar(pb,i)
    locid <- locids[i]
    build.df <- divvy_coding_ppa(locid)
    out.df <- rbind(out.df,build.df)
  }
  return(out.df)
}



```


```{r}

divvy.df <- build_coding_divvy_df()

aug.df <- inner_join(divvy.df,ppa.df,by="Locus.ID") %>% dplyr::select(.,-one_of("coding"))

write.table(aug.df,out.dir %&%"full_best-joint_ppa-prop_divvy-coding.txt",sep="\t",row.names=FALSE,quote=FALSE)


```


