---
title: "PCA and clustering analysis"
author: "Jason Torres"
date: "11/21/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Setup 

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("data.table")
library("tidyverse")
library("GenomicRanges")
library("viridis")

#serv.dir <- "/Users/jtorres/FUSE/"
serv.dir <- "/Users/jtorres/Google Drive/Science/" 
work.dir <- serv.dir %&% "Projects/t2d-integration/fgwas/diagram_hrc/cross_tissue/multi_tissue_joint_analysis/"
file.dir <- work.dir %&% "analysis_files/"
plot.dir <- work.dir %&% "plots/"

```


Read data files 

```{r}

block99.df <- fread(work.dir%&%"tempo_data/multi_results/results_blocks.txt",sep="\t")
fcred99.df <- fread(work.dir%&%"tempo_data/multi_results/results_func-cred-sets.txt",sep="\t")
full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
condensed.df <- fread(file.dir %&% "condensed_best-joint_ppa-prop.txt")



```


# PCA 

Uncentered analysis 

```{r}

loc.ids <- full.df$Locus.ID

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID")) %>% scale(.,center=FALSE,scale=FALSE)


pr.out <- prcomp(df,scale=FALSE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

```

Centered analysis 

```{r}

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df.cent <- dplyr::select(full.df,-one_of("Locus.ID")) %>% scale(.,center=TRUE,scale=TRUE)


pr.out.cent <- prcomp(df.cent,scale=TRUE)
pr.out.cent$sdev # standard deviations of each principal compoment
pr.var.cent <- pr.out.cent$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var.cent/sum(pr.var.cent)
cumulsum<- cumsum(pve)
cent.pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

```



Add more columns with plotting information 

```{r}

refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

```



## Proportion of Variance Explained Plot 


```{r}


scree_cumsum_plot <- function(pve.df){
  pltA <- ggplot(data=pve.df,aes(x=PC)) + 
    geom_line(aes(y=pve)) + 
    geom_point(aes(y=pve),size=3,shape=21,fill=rev(viridis(length(pve.df$PC)))) + 
    scale_y_continuous(limits=c(0,1),breaks=seq(0,1,0.1)) + 
    scale_x_continuous(limits=c(0,length(pve.df$PC)),breaks=seq(0,length(pve.df$PC),1)) + 
    theme_light() + 
    coord_cartesian(ylim=c(0,1),xlim=c(0.5,length(pve.df$PC)+0.5),expand=FALSE) + 
    xlab("Principal Component") + ylab("Proportion of Variance Explained") + 
    ggtitle("Variance explained by principal components") + 
    theme(panel.grid.minor = element_blank(),
          axis.title = element_text(size=8),
          plot.title = element_text(size=10))
  
  pltB <- ggplot(data=pve.df,aes(x=PC)) + 
    geom_line(aes(y=cumulsum)) + 
    geom_point(aes(y=cumulsum),size=3,shape=21,fill=rev(viridis(length(pve.df$PC)))) + 
    scale_y_continuous(limits=c(0,1),breaks=seq(0,1,0.1)) +
    scale_x_continuous(limits=c(0,length(pve.df$PC)),breaks=seq(0,length(pve.df$PC),1)) + 
    theme_light() + 
    coord_cartesian(ylim=c(0,1),xlim=c(0.5,length(pve.df$PC)+0.5),expand=FALSE) + 
    xlab("Principal Component") + ylab("Cumulative proportion of variance explained") + 
    ggtitle("Cumulative variance explained by principal components") + 
    theme(panel.grid.minor = element_blank(),
          axis.title = element_text(size=8),
          plot.title = element_text(size=10))

  grid.arrange(pltA,pltB,nrow=2)  
}

pltA <- scree_cumsum_plot(pve.df)
pltB <- scree_cumsum_plot(cent.pve.df)

ggsave(plot=pltA,filename=plot.dir%&%"pca_scree_cumsum_uncentered.png",
       height=6,width=4)
ggsave(plot=pltB,filename=plot.dir%&%"pca_scree_cumsum_centered.png",
       height=6,width=4)

```

Based on the scree plots will proceed with the uncentered data frame 

## Loading vector proportion plots 

```{r}

library("RColorBrewer")

loading_plot <- function(pr.output){
  numb <- dim(pr.output$rotation)[1]
  pca.prop.df <- pr.output$rotation %>% as.data.frame(.,row.names=FALSE)
  annot.vec <- gsub("_"," ",row.names(pr.output$rotation))
  pca.prop.df <- map(1:dim(pca.prop.df)[2],function(i){
    vec <- abs(as.numeric(pca.prop.df[,i])) # absolute value step 
    vec <- vec / sum(vec)
  }) %>% unlist(.) %>% matrix(.,nrow=numb,ncol=numb,byrow=FALSE) %>% as.data.frame(.)
  
  names(pca.prop.df) <- "PC" %&% 1:dim(pca.prop.df)[2]
  
  reformat.list <- map(1:dim(pca.prop.df)[1],function(i){
    PC <- names(pca.prop.df) %>% gsub("PC","",.) %>% as.integer(.)
    Score <- as.numeric(pca.prop.df[i,])
    #PC <- rep(i,length(Score))
    Annotation <- rep(annot.vec[i],length(Score))
    sub.df <- data.frame(PC,Score,Annotation,stringsAsFactors = FALSE)
  }) 
  
  out.df <- c()
  for (i in 1:length(reformat.list)){
    sub.df <- reformat.list[[i]]
    out.df <- rbind(out.df,sub.df)
  }
  ggplot(data=out.df,aes(x=PC,y=Score,fill=Annotation)) + 
          geom_bar(stat="identity",color="black",size=0.2) + 
          scale_y_continuous(breaks=seq(0,1,0.1)) + 
          scale_x_continuous(breaks=seq(0,length(unique(out.df$PC)),1)) + 
          scale_fill_manual(values=colorRampPalette(brewer.pal(11,                                  "Spectral"))(length(unique(out.df$PC)) )) + 
          ggtitle("PC Loading Scores for Genomic Annotations") + 
          ylab("Loading Proportion")
}

pltLA <- loading_plot(pr.out)
pltLB <- loading_plot(pr.out.cent)

ggsave(plot=pltLA,filename=plot.dir%&%"pca_loading_uncentered.png",
       height=6,width=8)
ggsave(plot=pltLB,filename=plot.dir%&%"pca_loading_centered.png",
       height=6,width=8)

```


## PCA plots 


```{r}

library("ggrepel")

pca_annotated_plot <- function(data.df,pca.out,pcX,pcY,annot){
  pca.df <- as.data.frame(pca.out$x) 
  pca.df$Locus.ID <- data.df$Locus.ID
  pca.df <- inner_join(data.df,pca.df,by="Locus.ID")
  
  index <- match(annot,names(pca.df))
  vec <- pca.df[,index]
  names(vec) <- pca.df$Plot.ID
  keep.vec <- sort(vec,decreasing=TRUE)[1:10]
  keep.names <- names(keep.vec)
  
  sub.df <- filter(pca.df,Plot.ID %in% keep.names)
  
  ggplot(data=pca.df,aes_string(x=pcX,y=pcY)) + 
    geom_point(shape=21,size=2,color="black",
               aes_string(fill=annot)) +
    scale_fill_viridis(option="plasma") + 
    geom_label_repel(data=sub.df,
                     aes_string(x=pcX,y=pcY,label="Plot.ID"),
                     size=1.5,
                     fontface="bold",
                     fill="ghostwhite",
                     box.padding = unit(0.1,"lines"), 
                     point.padding = unit(0.1,"lines"),
                     alpha=0.7,label.size=0.1) + 
    theme_bw()  
}


pcpltA <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","distance_tss_0_5000")
ggsave(plot=pcpltA,filename=plot.dir%&%"pca_uncentered_pc1_pc2_dist.png",height=4,width=6)

pcpltB <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_shared_repressed")
ggsave(plot=pcpltB,filename=plot.dir%&%"pca_uncentered_pc1_pc2_isl-shar-rep.png",height=4,width=6)

pcpltC <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","other")
ggsave(plot=pcpltC,filename=plot.dir%&%"pca_uncentered_pc1_pc2_other.png",height=4,width=6)

pcpltD <- pca_annotated_plot(full.df,pr.out,"PC3","PC4","islet_shared_strong_enhancer")
ggsave(plot=pcpltD,filename=plot.dir%&%"pca_uncentered_pc3_pc4_isl-shar-strenh.png",height=4,width=6)

pcpltE <- pca_annotated_plot(full.df,pr.out,"PC3","PC4","islet_specific_strong_enhancer")
ggsave(plot=pcpltE,filename=plot.dir%&%"pca_uncentered_pc3_pc4_isl-spec-strenh.png",height=4,width=6)

```

Centered 


```{r}

pcpltAA <- pca_annotated_plot(full.df,pr.out.cent,"PC1","PC2","distance_tss_0_5000")
ggsave(plot=pcpltAA,filename=plot.dir%&%"pca_centered_pc1_pc2_dist.png",height=4,width=6)

```


## Removing TSS distance from PCA analysis 

Uncentered analysis 

```{r}

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID","distance_tss_0_5000","coding")) %>% scale(.,center=FALSE,scale=FALSE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

pr.out <- prcomp(df,scale=FALSE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

pltA2 <- scree_cumsum_plot(pve.df)
ggsave(plot=pltA2,filename=plot.dir%&%"pca_scree_cumsum_uncentered_NODIST.png",
       height=6,width=4)

pltLA3 <- loading_plot(pr.out)
ggsave(plot=pltLA3,filename=plot.dir%&%"pca_loading_uncentered_NODIST.png",
       height=6,width=8)

pcpltB2 <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_shared_repressed")
ggsave(plot=pcpltB2,filename=plot.dir%&%"pca_uncentered_pc1_pc2_isl-shar-rep_NODIST.png",height=4,width=6)

pcpltC2 <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","other")
ggsave(plot=pcpltC2,filename=plot.dir%&%"pca_uncentered_pc1_pc2_other_NODIST.png",height=4,width=6)

pcpltD2 <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_specific_strong_enhancer")
ggsave(plot=pcpltD2,filename=plot.dir%&%"pca_uncentered_pc1_pc2_isl-spec-strenh_NODIST.png",height=4,width=6)

```



## Removing only islet_shared_repressed (Uncentered/unscaled)

```{r}

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID","islet_shared_repressed")) %>% scale(.,center=FALSE,scale=FALSE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

pr.out <- prcomp(df,scale=FALSE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

pltA <- scree_cumsum_plot(pve.df)
ggsave(plot=pltA,filename=plot.dir%&%"pca_scree_cumsum_uncentered_NO-ISR.png",
       height=6,width=4)

pltB <- loading_plot(pr.out)
ggsave(plot=pltB,filename=plot.dir%&%"pca_loading_uncentered_NO-ISR.png",
       height=6,width=8)

pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","distance_tss_0_5000")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc1_pc2_disttss_NO-ISR.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","other")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc1_pc2_other_NO-ISR.png",height=4,width=6)

```


## Removing distance, coding, islet_shared_repressed, and other  (Uncentered/unscaled)

```{r}

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID","islet_shared_repressed","distance_tss_0_5000",
                                    "coding","other")) %>% scale(.,center=FALSE,scale=FALSE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

pr.out <- prcomp(df,scale=FALSE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

pltA <- scree_cumsum_plot(pve.df)
ggsave(plot=pltA,filename=plot.dir%&%"pca_scree_cumsum_uncentered_NO-ISR-dist-coding-other.png",
       height=6,width=4)

pltB <- loading_plot(pr.out)
ggsave(plot=pltB,filename=plot.dir%&%"pca_loading_uncentered_No-ISR-dist-coding-other.png",
       height=6,width=8)

pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_shared_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc1_pc2_isl-shar-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_specific_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc1_pc2_isl-spec-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC3","PC6","adipose_specific_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc3_pc6_adi-spec-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC3","PC6","muscle_specific_weak_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_uncentered_pc3_pc6_mus-spec-weakenh_NO-ISR-dist-coding-other.png",height=4,width=6)
```


## Removing distance, coding, islet_shared_repressed, and other  (centered/scaled)

```{r}

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID","islet_shared_repressed","distance_tss_0_5000",
                                    "coding","other")) %>% scale(.,center=TRUE,scale=TRUE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

pr.out <- prcomp(df,scale=TRUE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

pltA <- scree_cumsum_plot(pve.df)
ggsave(plot=pltA,filename=plot.dir%&%"pca_scree_cumsum_centered_NO-ISR-dist-coding-other.png",
       height=6,width=4)

pltB <- loading_plot(pr.out)
ggsave(plot=pltB,filename=plot.dir%&%"pca_loading_centered_No-ISR-dist-coding-other.png",
       height=6,width=8)

pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_shared_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_isl-shar-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_specific_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_isl-spec-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","adipose_specific_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_adi-spec-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","liver_specific_strong_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_liv-spec-strenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","muscle_specific_weak_enhancer")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_mus-spec-weakenh_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_specific_bivalent_tss")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_isl-spec-bivtss_NO-ISR-dist-coding-other.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_shared_promoter")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_isl-share-strprom_NO-ISR-dist-coding-other.png",height=4,width=6)

```

## COMPACT DATA FRAME ANALYSIS: Removing distance, coding, islet_shared_repressed, and other  (centered/scaled)

```{r}

full.df <- fread(file.dir %&% "compact_best-joint_ppa-prop.txt")
df <- dplyr::select(compact.df,-one_of("Locus.ID","islet_shared_repressed","distance_tss_0_5000",
                                    "coding","other")) %>% scale(.,center=TRUE,scale=TRUE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
full.df$refseq <- refseq
full.df$Plot.ID <- full.df$Locus.ID %&% ": " %&% full.df$refseq

pr.out <- prcomp(df,scale=TRUE)
pr.out$sdev # standard deviations of each principal compoment
pr.var <- pr.out$sdev^2 # Getting the variance explained by each PC 
pve<-pr.var/sum(pr.var)
cumulsum<- cumsum(pve)
pve.df <- data.frame(PC=c(1:length(pve)),pve,cumulsum)

pltA <- scree_cumsum_plot(pve.df)
ggsave(plot=pltA,filename=plot.dir%&%"pca_scree_cumsum_centered_COMPACT.png",
       height=6,width=4)

pltB <- loading_plot(pr.out)
ggsave(plot=pltB,filename=plot.dir%&%"pca_loading_centered_COMPACT.png",
       height=6,width=8)

pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","adipose")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_adipose_COMPACT.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_regulatory")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_isl-reg_COMPACT.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","liver")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_liver_COMPACT.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","muscle")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_muscle_COMPACT.png",height=4,width=6)
pcplt <- pca_annotated_plot(full.df,pr.out,"PC1","PC2","islet_bivalent_tss")
ggsave(plot=pcplt,filename=plot.dir%&%"pca_centered_pc1_pc2_islt-biv_COMPACT.png",height=4,width=6)


```




# Hierarchical clustering 




```{r}

library("ggdendro")

full.df <- fread(file.dir %&% "full_best-joint_ppa-prop.txt")
df <- dplyr::select(full.df,-one_of("Locus.ID","islet_shared_repressed","distance_tss_0_5000",
                                    "coding","other")) %>% scale(.,center=TRUE,scale=TRUE) %>% as.data.frame(.,stringsAsFactors=TRUE)
refseq <- map(1:dim(full.df)[1],function(i){
  loc <- full.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
df$refseq <- refseq
df$Plot.ID <- full.df$Locus.ID %&% ": " %&% df$refseq

dist.df <- dplyr::select(df,-one_of("refseq","Plot.ID")) %>% as.data.frame(.)
row.names(dist.df) <- df$Plot.ID

#dist.df <- dist.df[1:60,]
dist.df <- dist.df[1:406,]

data.dist <- dist(dist.df)
plot(hclust(data.dist),main="Complete Linkage",xlab="",ylab="")


hc <- hclust(dist(dist.df),method = "complete")
#ggdendrogram(hc,rotate=FALSE,size=2)

dhc <- as.dendrogram(hc)
ddata <- dendro_data(dhc,type="rectangle")
lab.df <- label(ddata)

Max.Annot <- as.character(map(as.character(lab.df$label),function(id){
  i <- match(id,row.names(dist.df))
  vec <- dist.df[i,]
  vecmax <- max(vec)
  coli <-match(vecmax,vec)
  maxannot <- names(dist.df)[coli]
  return(maxannot)
}))

lab.df$Max.Annot <- Max.Annot

p <- ggplot(segment(ddata)) + 
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) + 
  coord_flip() + 
  geom_label(data=lab.df,aes(x=x,y=y-4,label=label,fill=Max.Annot),
             label.size=0.1,size=2) + 
  scale_y_reverse(expand = c(0.2, 0)) + 
  scale_fill_brewer(palette="Spectral") + 
  theme_bw()
#ggsave(plot=p,filename=plot.dir%&%"cluster_scaled_dummy.png",height=15,width=15,limitsize=FALSE)
ggsave(plot=p,filename=plot.dir%&%"cluster_scaled.png",height=40,width=10,limitsize=FALSE)
```

## COMPACT 

```{r}

library("ggdendro")

compact.df <- fread(file.dir %&% "compact_best-joint_ppa-prop.txt")
df <- dplyr::select(compact.df,-one_of("Locus.ID","islet_shared_repressed","distance_tss_0_5000",
                                    "coding","other")) %>% scale(.,center=TRUE,scale=TRUE) %>% as.data.frame(.,stringsAsFactors=TRUE)
refseq <- map(1:dim(compact.df)[1],function(i){
  loc <- compact.df$Locus.ID[i]
  gene <- filter(block99.df,Locus.ID==loc)$refseq
}) %>% as.character(.)
df$refseq <- refseq
df$Plot.ID <- compact.df$Locus.ID %&% ": " %&% df$refseq

dist.df <- dplyr::select(df,-one_of("refseq","Plot.ID")) %>% as.data.frame(.)
row.names(dist.df) <- df$Plot.ID

#dist.df <- dist.df[1:60,]
dist.df <- dist.df[1:406,]

data.dist <- dist(dist.df)
plot(hclust(data.dist),main="Complete Linkage",xlab="",ylab="")


hc <- hclust(dist(dist.df),method = "complete")
#ggdendrogram(hc,rotate=FALSE,size=2)

dhc <- as.dendrogram(hc)
ddata <- dendro_data(dhc,type="rectangle")
lab.df <- label(ddata)

Max.Annot <- as.character(map(as.character(lab.df$label),function(id){
  i <- match(id,row.names(dist.df))
  #vec <- dist.df[i,]
  vec <- compact.df[i,2:dim(compact.df)[2]]
  vecmax <- max(vec)
  coli <-match(vecmax,vec)
  #maxannot <- names(dist.df)[coli]
  maxannot <- names(compact.df)[coli+1]
  return(maxannot)
}))

lab.df$Max.Annot <- Max.Annot

p <- ggplot(segment(ddata)) + 
  geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) + 
  coord_flip() + 
  geom_label(data=lab.df,aes(x=x,y=y-4,label=label,fill=Max.Annot),
             label.size=0.1,size=2) + 
  scale_y_reverse(expand = c(0.2, 0)) + 
  scale_fill_brewer(palette="Spectral") + 
  theme_bw()

 #ggsave(plot=p,filename=plot.dir%&%"cluster_scaled_dummy_COMPACT.png",height=15,width=15,limitsize=FALSE)
 ggsave(plot=p,filename=plot.dir%&%"cluster_scaled_COMPACT_updated.png",height=40,width=20,limitsize=FALSE)
 
 #
```





