---
title: "01.1_tactical-toa-scores.Rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

```{r}

"%&%" <- function(a,b) paste0(a,b)
library("tidyverse")
library("data.table")

serv.dir <- "/home/jason/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <- proj.dir %&% "tactical_analyses/"
input.dir <- work.dir %&% "input_files/"
file.dir <- work.dir %&% "analysis_files/"

```


```{r}

toa.dt <- fread(file.dir%&%"classified-loci_weighted_with-shared.txt")
toa.dt1 <- fread(file.dir%&%"classified-loci_weighted_with-shared_v1.txt")
toa.dt2 <- fread(file.dir%&%"classified-loci_weighted_with-shared_v2.txt")
toa.dt3 <- fread(file.dir%&%"classified-loci_weighted_with-shared_ALT.txt")
```


```{r}
sum(toa.dt$assigned_00==toa.dt1$assigned_00) # 380 
sum(toa.dt$assigned_20==toa.dt1$assigned_20) # 380
sum(toa.dt$assigned_50==toa.dt1$assigned_50) # 380
sum(toa.dt$assigned_80==toa.dt1$assigned_80) # 380 
```


Using the original and updated ESS input files does not effect the tissue classifications in any way! So no worries on that front; 


```{r}

sum(toa.dt1$assigned_00==toa.dt2$assigned_00) # 378 
sum(toa.dt1$assigned_20==toa.dt2$assigned_20) # 378
sum(toa.dt1$assigned_50==toa.dt2$assigned_50) # 379
sum(toa.dt1$assigned_80==toa.dt2$assigned_80) # 380  

```

Including an additional 60 samples only changes the classification of 1-2 signals, from the 0.5 threshold and below 


```{r}

toa.dt[toa.dt$assigned_00!=toa.dt2$assigned_00]
toa.dt1[toa.dt1$assigned_00!=toa.dt2$assigned_00]
toa.dt2[toa.dt1$assigned_00!=toa.dt2$assigned_00]

```

Including an additional 60 islet samples had the following effects on two signals 
1) changed GPSM1 signal (125_2) from "islet" (islet toa=0.3440; adipose toa=0.2439) to "shared"(islet toa=0.3408; adipose toa = 0.2463). NOTE that this signal was barely over the shared threshold (toa difference >= 0.10) to begin with.
2) changed NEUROG3 signal (127_4) from "shared" (adipose toa=0.3562; islet toa=0.4524) to "adipose" (adipose=0.5071; islet toa=0.3014) signal; this change was more considerable but was the only occurance out of 380 signals, so I don't think changes the substance of the paper as we've already addressed relevant shortcoming in the dicussion and would not expect this to dramatically alter the validation/enrichment anlayses 



Checking against the alternative logarithmic weighting scheme 

```{r}
sum(toa.dt$assigned_00==toa.dt3$assigned_00) # 348 
sum(toa.dt$assigned_20==toa.dt3$assigned_20) # 348
sum(toa.dt$assigned_50==toa.dt3$assigned_50) # 363
sum(toa.dt$assigned_80==toa.dt3$assigned_80) # 377 
```


```{r}
toa.dt[toa.dt$assigned_00!=toa.dt3$assigned_00] %>% head(.)
toa.dt3[toa.dt3$assigned_00!=toa.dt$assigned_00] %>% head(.)

toa.dt$assigned_00[toa.dt$assigned_00!=toa.dt3$assigned_00]
toa.dt3$assigned_00[toa.dt$assigned_00!=toa.dt3$assigned_00]

```




