---
title: "physiology-loci-enrichment.Rmd"
author: "Jason Torres"
date: "5/13/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup


```{r}

set.seed(100)

"%&%" <- function(a,b) paste0(a,b)
library("tidyverse")
library("data.table")
serv.dir <- "/home/jason/science/servers/FUSE5/"
proj.dir <- serv.dir %&% "projects/t2d_classification/"
work.dir <-  proj.dir %&% "tactical_analyses/" 
cred.df <- fread(work.dir %&% "genetic_credible_sets/gencred.txt")
write.dir <- work.dir   
phys82.df <- fread(work.dir %&% "analysis_files/phys94-ld-assigned.txt") %>%
  filter(.,assigned.r2>=0.3) # fuzzy 
phys73.df <- fread(work.dir %&% "analysis_files/phys94-ld-assigned.txt") %>%
  filter(.,assigned.r2>=0.5) # fuzzy 
phys53.df <- fread(work.dir %&% "analysis_files/phys94-ld-assigned.txt") %>%
  filter(.,assigned.r2>=0.8) # fuzzy 
```


Also consider the set of HRC 71 SNPs from Anubha
```{r}

phys71.df <- fread(work.dir %&% "analysis_files/physiology_hrc_for_Jason.txt")
names(phys71.df)[1] <- "Locus.ID"
phys71.df$Locus.ID <- map(phys71.df$Locus.ID,function(s){
  if (grepl("_",s)==FALSE){
    s <- s %&% "_1"
  }
  return(s)
}) %>% as.character(.)

```



```{r}

keep.sigs <- filter(cred.df,PPA>=0.5)$CondID

weighted.df <- fread(work.dir %&% "analysis_files/" %&% 
                     "classified-loci_weighted_with-shared.txt") %>% filter(.,Locus.ID %in% keep.sigs)
```



# Enrichment functions 

```{r}

enrich_test <- function(query.vec,ref.vec,iter=10000){
  vec <- cred.df$CondID %>% unique(.)
  obs <- (query.vec %in% ref.vec) %>% sum(.)
  null.vec <- c()
  pb <- txtProgressBar(min=0,max=iter,style=3)
  for (i in 1:iter){
    setTxtProgressBar(pb,i)
    samp <- sample(x=vec,size=length(query.vec),replace=FALSE)
    count <- (samp %in% ref.vec) %>% sum(.)
    null.vec <- append(null.vec,count)
  }
  enrichment <- obs/(mean(null.vec))
  p <- (sum(null.vec >= obs) + 1) / (iter + 1)
  out.df <- data.frame(observed.count=obs,mean.null=mean(null.vec),
                       enrichment=enrichment,p=p,stringsAsFactors = FALSE)
  return(out.df)
}

build_enrich_df <- function(class.df,phys.df){
  tvec <- c("assigned_00","assigned_20","assigned_50","assigned_80")
  tiss.vec <- c("islet","liver","adipose","muscle","shared","peripheral")
  phys.vec <- phys.df$Physiology  %>% unique(.)
  out.df <- c()
  for (t in tvec){
    cond <- "Locus.ID"
    threshold <- t
    sub <- dplyr::select(class.df,one_of(cond,threshold))
    names(sub)[2] <- "assigned"
    for (tiss in tiss.vec){
      if (tiss=="peripheral"){
        query.vec <- filter(sub,assigned!="islet")$Locus.ID %>% unique(.)
      } else{
        query.vec <- filter(sub,assigned==tiss)$Locus.ID %>% unique(.)
      }
      for (phys in phys.vec){
        print("Threshold: " %&% t %&% " Tissue: " %&% tiss %&% " Physiology: " %&% phys)
        ref.vec <- filter(phys.df,Physiology==phys)$Locus.ID %>% 
          unique(.)
        test.df <- enrich_test(query.vec,ref.vec,iter=10000)
        test.df$threshold <- threshold; test.df$tissue <- tiss
        test.df$physiology <- phys
        test.df <- dplyr::select(test.df,one_of("tissue","physiology",
                                                "observed.count",
                                                "mean.null",
                                                "enrichment","p",
                                                "threshold"))
        out.df <- rbind(out.df,test.df)
      }
    }
  }
  return(out.df)
}


```


```{r}

# Fuzzy; r2 > 0.3
df82 <- build_enrich_df(weighted.df,phys82.df)
write.table(x=df82,file = write.dir %&% "analysis_files/" %&% 
              "phys82-enrich_weighted_with-shared_set101.txt",
            sep="\t",quote=F,row.names=F)
# Fuzzy; r2 > 0.5
df73 <- build_enrich_df(weighted.df,phys73.df)
write.table(x=df73,file = write.dir %&% "analysis_files/" %&% 
              "phys73-enrich_weighted_with-shared_set101.txt",
            sep="\t",quote=F,row.names=F)
# Fuzzy; r2 > 0.8
df53 <- build_enrich_df(weighted.df,phys53.df)
write.table(x=df53,file = write.dir %&% "analysis_files/" %&% 
              "phys53-enrich_weighted_with-shared_set101.txt",
            sep="\t",quote=F,row.names=F)
# Hard
df71 <- build_enrich_df(weighted.df,phys71.df) # Not sure if this is fuzzy or hard clustering
write.table(x=df71,file = write.dir %&% "analysis_files/" %&% 
              "phys71-enrich_weighted_with-shared_set101.txt",
            sep="\t",quote=F,row.names=F)

filter(df82,p<0.05,threshold!="assigned_00") %>% arrange(.,p)
filter(df73,p<0.05,threshold!="assigned_00") %>% arrange(.,p)
filter(df53,p<0.05,threshold!="assigned_00") %>% arrange(.,p)

filter(df71,p<0.05,threshold!="assigned_00") %>% arrange(.,p)


```

Note that among the 101 most fine-mapped signals, only islet and liver yield significant enrichemtns 
For example:
filter(df82,p<0.05,threshold!="assigned_00") %>% arrange(.,p)
  tissue   physiology observed.count mean.null enrichment          p   threshold
1  liver Dyslipidemia              2    0.0803  24.906600 0.00169983 assigned_50
2  liver Dyslipidemia              2    0.0861  23.228804 0.00239976 assigned_20
3  islet         IS-1              2    0.1417  14.114326 0.00659934 assigned_80
4  islet         IS-1              3    0.5094   5.889282 0.00939906 assigned_20
5  islet         IS-1              2    0.2837   7.049700 0.02509749 assigned_50
6  islet         IS-2              5    1.8650   2.680965 0.02949705 assigned_20

# Physiology driven enrichment (see if phys groups are enriched for higher tissue scores)


```{r}

enrich_test_v2 <- function(phys.vec, tissue, class.df,iter=10000){
  if (tissue == "peripheral"){
    full.vec <- dplyr::select(class.df,one_of("liver","muscle","adipose")) %>% rowSums(.)
    query.vec <- filter(class.df,Locus.ID%in%phys.vec) %>% dplyr::select(.,one_of("liver","muscle","adipose")) %>% rowSums(.)
  } else{
    full.vec <- dplyr::select(class.df,one_of(tissue)) %>% as.matrix(.) %>% as.numeric(.)
    query.vec <- filter(class.df,Locus.ID%in%phys.vec) %>% dplyr::select(.,one_of(tissue)) %>% as.matrix(.) %>% as.numeric(.)
  }
  obs.mean <- mean(query.vec)
  null.vec <- c()
  pb <- txtProgressBar(min=0,max=iter,style=3)
  for (i in 1:iter){
    setTxtProgressBar(pb,i)
      null.vec <- append(null.vec,sample(x=full.vec,size=length(query.vec),replace=TRUE) %>% mean(.))
  }
  enrichment <- obs.mean / mean(null.vec)
  p <- (sum(null.vec >= obs.mean) + 1) / (iter + 1)
  out.df <- data.frame(obs.mean=obs.mean,null.mean=mean(null.vec),enrichment=enrichment,p=p,stringsAsFactors = F)
}


build_enrich_df_v2 <- function(class.df,phys.df){
  tiss.vec <- c("islet","liver","adipose","muscle","peripheral")
  phys.vec <- phys.df$Physiology  %>% unique(.)
  out.df <- c()
  for (phys in phys.vec){
    query.vec <- filter(phys.df,Physiology==phys)$Locus.ID %>% 
      unique(.)    
    for (tiss in tiss.vec){
      test.df <- enrich_test_v2(query.vec,tiss,class.df,iter=10000)
      test.df$tissue <- tiss; test.df$physiology <- phys
      test.df <- dplyr::select(test.df,one_of("physiology","tissue",
                                              "obs.mean",
                                              "null.mean",
                                              "enrichment","p"))
      out.df <- rbind(out.df,test.df)
    }
  }
  return(out.df)
}


```


```{r}

df82b <- build_enrich_df_v2(weighted.df,phys82.df)
write.table(x=df82b,file = write.dir %&% "analysis_files/" %&% 
              "phys-enrich82_weighted-V2_set101.txt",sep="\t",quote=F,row.names=F)
filter(df82b,p<0.05) %>% arrange(.,p) #%>% View(.)

df73b <- build_enrich_df_v2(weighted.df,phys73.df)
write.table(x=df73b,file = write.dir %&% "analysis_files/" %&% 
              "phys-enrich73_weighted-V2_set101.txt",sep="\t",quote=F,row.names=F)
filter(df73b,p<0.05) %>% arrange(.,p) #%>% View(.)

df53b <- build_enrich_df_v2(weighted.df,phys53.df)
write.table(x=df53b,file = write.dir %&% "analysis_files/" %&% 
              "phys-enrich53_weighted-V2_set101.txt",sep="\t",quote=F,row.names=F)
filter(df53b,p<0.05) %>% arrange(.,p) #%>% View(.)

df71b <- build_enrich_df_v2(weighted.df,phys71.df)
write.table(x=df71b,file = write.dir %&% "analysis_files/" %&% 
              "phys-enrich71_weighted-V2_set101.txt",sep="\t",quote=F,row.names=F)
filter(df71b,p<0.05) %>% arrange(.,p) #%>% View(.)

```


It appears that adjusting the r2 threshold from 0.3, to 0.5, to 0.8, does not change the substance of the results for the fuzzy clustering; not sure if its worth changing or better to leave as is (i.e. 0.3 threshold)













